When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-06-14 06_Paper/COG-ED/Stage 2/Supplement.Rmd
added contrast plot + h3ac + h3b plots

@@

@@

>>>>

## Contrasts tested for in the repeated measures ANOVA

```{r contrast-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Contrasts tested for in the repeated measures ANOVA that was used as a prerequisite for the multi level model of hypothesis 2b. Ascending quadratic (-1,1,1,-1), declining linear (3,1,-1,-3), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2). Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "contrasts.png"))

@@

```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back. Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges. NFC = Need for Cognition score. $N=116$. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3ac-plot.png"))

@@

```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level. Colours indicate Need for Cognition (NFC) score above or below the median. $N=116$. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3b-plot.png"))
